Scheeper's Meager-NWD Game and the Menger Game

### 2014-11-26 phd/dissertation/chapter5.tex
finish k-space results

A variation of $\gruConGame{X}{x}$, also due to Gruenhage,
may be used to characterize various covering properties, particularly
for locally compact spaces. We assume all spaces are $T_1$.

@@

\begin{defn}
  A space $X$ is \term{compactly generated} if a set is closed if and
  only if its intersection is closed in every compact subspace. Such
  spaces are also known as \term{$k$-spaces}.
\end{defn}

@@

\begin{defn}
  A space $X$ is a $k_\omega$-space if there exist compact sets $K_n$ for
  $n<\omega$ such that a set is closed if and
  only if its intersection is closed in every subspace $K_n$.
\end{defn}

\begin{thm}
  If $X$ is a Hausdorff hemicompact $k$-space, then
  $\pl K \prewin \gruKLGame{X}$.
\end{thm}

\begin{proof}
  Let $K_n$ witness hemicompactness for $X$. Define the predetermined strategy
  $\sigma$ for $\pl K$ by $\sigma(n)=K_n$.

  Let $L:\omega\to\mc{K}(X)$ be a legal attack against $\sigma$, and let
  $L_\omega = \bigcup_{n<\omega}L_(n)$. For each compact set (TODO FINISH)
\end{proof}

\begin{cor}
  The following are equivalent for any Hausdorff $k$-space $X$:
    \begin{itemize}
      \item $X$ is hemicompact.
      \item $X$ is $k_{\omega}$.
      \item $\pl K \prewin \gruKPGame{X}$.
      \item $\pl K \prewin \gruKLGame{X}$.
    \end{itemize}
\end{cor}

>>>>

A variation of $\gruConGame{X}{x}$, also due to Gruenhage,
may be used to characterize various covering properties, particularly
for locally compact spaces. All spaces are assumed to be $T_1$ in this
chapter.

@@

\begin{defn}
  A space $X$ is \term{compactly generated} if a set is closed if and
  only if its intersection with every compact set is closed. Such
  spaces are also known as \term{$k$-spaces}.
\end{defn}

@@

\begin{defn}
  A space $X$ is a $k_\omega$-space if there exist compact sets $K_n$ for
  $n<\omega$ such that a set is closed if and
  only if its intersection with every $K_n$ is closed.
\end{defn}

\begin{thm}
  If $X$ is a $k_\omega$-space, then
  $\pl K \prewin \gruKLGame{X}$.
\end{thm}

\begin{proof}
  Let $K_n$ witness that $X$ is a $k_\omega$-space. Define the predetermined
  strategy $\sigma$ for $\pl K$ by $\sigma(n)=K_n$.

  Let $L:\omega\to\mc{K}(X)$ be a legal attack against $\sigma$, and let
  $L_{\omega\setminus n} = \bigcup_{n\leq m<\omega}L(m)$. Then as
    \[
      L_{\omega\setminus n}\cap K_n
        =
      \bigcup_{n\leq m< p}L(m) \cap \sigma(p)
    \]
  is compact for each $p<\omega$, $L_{\omega\setminus n}$ is closed.

  For each $x\in X$, $x\in \sigma(p)$ for some $p$, so
  $x\in X\setminus L_{\omega\setminus p}$ which misses all but finitely
  many $L(n)$, showing that $\{L(n):n<\omega\}$ is locally finite and
  $\sigma$ is a winning predetermined strategy.
\end{proof}

\begin{prop}
  Hemicompact $k$-spaces are $k_\omega$-spaces.
\end{prop}

\begin{proof}
  Let $K_n$ for $n<\omega$ witness hemicompactness.
  If $C\cap K_n$ is closed for each $n<\omega$, then let $K$ be any compact
  set. Since $K\subseteq K_n$ for some $n<\omega$, $C\cap K$ is closed, and
  therefore $C$ is closed.
\end{proof}

As we've already seen that $\pl K \prewin \gruKPGame{X}$ implies
hemicompactness:

\begin{cor}
  The following are equivalent for any $k$-space $X$:
    \begin{itemize}
      \item $X$ is $k_{\omega}$.
      \item $X$ is hemicompact.
      \item $\pl K \prewin \gruKPGame{X}$.
      \item $\pl K \prewin \gruKLGame{X}$.
    \end{itemize}
\end{cor}
